Analisis de personas Indigenas que llegaron a UCI

### 2023-07-31 paper.tex
modificación del abstract

\usepackage[spanish]{babel}
%\usepackage[spanish]{babel}
\newenvironment{keywords}
{\par\small\textbf{Keywords}}
{\par}
%
% if BibLaTeX is used
%
\ifboolexpr{bool{jacowbiblatex}}%
 {%
  \addbibresource{jacow-test.bib}
  \addbibresource{biblatex-examples.bib}
 }{}
\listfiles

@@

%
\begin{abstract}
The objective of this article is to analyze the data of cases associated with COVID-19 in Mexico by applying segmentation techniques such as K-means, autoencoder and PCA, comparing them to search for demographic patterns in patients diagnosed with COVID-19.
The combination of advanced data analysis techniques will allow us to explore the complexity of the data, identify underlying patterns and obtain valuable information for decision making.
Also, by gaining a deeper insight into the COVID-19 data, we will be able to better understand the factors that contributed to the spread of the disease, the effectiveness of control measures, and the disparities across different population groups (indigenous and non-indigenous). natives).
In conclusion, this scientific article focuses on the analysis of information on Covid-19 in Mexico using techniques such as K-means, autoencoder and PCA.
\end{abstract}

\begin{keywords}
COVID-19, Mexico, analysis of data, segmentation, patterns, dimensionality reduction, PCA.
\end{keywords}

>>>>

\newenvironment{keywords}
{\par\small\textbf{Keywords}}
{\par}
%
% if BibLaTeX is used
%
\ifboolexpr{bool{jacowbiblatex}}%
 {%
  \addbibresource{jacow-test.bib}
  \addbibresource{biblatex-examples.bib}
 }{}
\listfiles

@@

%
\begin{abstract}
The combination of advanced data analysis techniques allow us to explore the complexity of the data, identify underlying patterns and obtain valuable information for decision making.
The objective of this article is to segment the data associated with COVID-19 cases in Mexico in order to find demographic patterns in the patients who attended a care center.
A comparison will be made between the influence of clustering proposals with dimensionality reduction and without dimensionality reduction on the segmentation of these patterns.
Also, by gaining a deeper insight into the COVID-19 data, we will be able to better understand the factors that contributed to the spread of the disease, and the disparities across different population groups (indigenous and non-indigenous). 
This article focuses on the analysis of information on Covid-19 in Mexico using techniques such as K-means, autoencoder and PCA.
\end{abstract}

\begin{keywords}
COVID-19, Mexico, analysis of data, segmentation, patterns, autoencoder, dimensionality reduction, PCA.
\end{keywords}
